### 2016-08-19 rebuttal.tex

\question In lines 543 and 545, ``rad'' should be removed. Radians are assumed when no other measure (like degrees) is given.
\begin{solution}
These units were removed.
\end{solution}

\question In lines 567--568, ``performing symbolic quantum mechanics'' makes no sense. This should probably be ``computations'', ``solving problems related to'', etc.
\begin{solution}

\end{solution}

\question The sentence ``SymPy expressions are immutable trees of Python objects.'' doesn't belong in the conclusion. This can be moved to the appropriate place when discussing SymPy's architecture.
\begin{solution}
This paper focuses on the architecture of SymPy, and we consider this to be a
core feature of SymPy's architecture, hence, it's inclusion in the conclusion.
We have also discussed the different points in this sentence in-depth in the architecture section.
\end{solution}

@@

\question All ``submodules'' should be replaced by ``modules'' (examples:
lines 657, 662).
\label{rev1point37}
\begin{solution}
We are unclear how the reviewer is making distinctions between ``modules'',
``submodules'', and ``packages''. Our use coincides with the definitions used
in the official Python documentation (see
\url{https://docs.python.org/3/tutorial/modules.html#packages} and
\url{https://docs.python.org/3/glossary.html#term-package}). The distinction
between (sub)module and (sub)package in terms of Python libraries seems very
technical. To clarify things, we have modified the manuscript to use
``package'' only when referring to a library external to SymPy (such as
mpmath and Xy-pic).

To avoid confusion, and to be consistent with the definitions used by the
official Python documentation, we have modified the manuscript to use
``submodule'' to refer to any module that is a dotted submodule of
\texttt{sympy}, such as \texttt{sympy.physics.quantum}. This is to emphasize
that these modules all live within the \texttt{sympy} namespace, as ``module''
can suggest a separate library.
\end{solution}

\question The sentences in lines 657--661 should swap places, because ``areas of mathematics'' are discrete mathematics, concrete mathematics, etc., while simplifying expressions, performing common calculus operations, pretty printing expressions, etc.\ belongs to common operations (``other areas'' is also fine, albeit slightly wrong).
\begin{solution}
The ``areas of mathematics'' was intended to encompass all mathematical
operations. We have rewritten the first sentence as
\begin{quote}
SymPy supports a wide array of mathematical facilities.
\end{quote}
We also changed ``other included areas'' to ``other supported facilities'' in the third sentence.

The order of the subsequence sentences was chosen to match the order they were
presented in the paper, so we have left them as-is.
\end{solution}

### 2016-08-19 conclusion_and_future_work.tex
Revert "Removed sentence, see question 36"
This reverts commit 214a695f591f0da43888338bd01ab63af14ecfe3.
Get rid of "areas of mathematics" in conclusion (reviewer 3, point 38)

SymPy uses Python both
as the internal language and the user language. This permits users to access to
the same
methods that the library implements in order to extend it for their needs.
Additionally, SymPy has a powerful assumptions
system for declaring and deducing mathematical properties of expressions.

SymPy has submodules for many areas of mathematics. This includes functions for
simplifying expressions, performing common calculus operations, pretty printing
expressions, solving equations, and representing symbolic matrices. Other included
areas
are discrete math, concrete math, plotting, geometry, statistics,
polynomials, sets, series, vectors, combinatorics, group theory, code
generation, tensors, Lie algebras, cryptography, and special functions.
Additionally, SymPy contains submodules targeting certain specific domains,
such as classical mechanics and quantum mechanics.  This breadth of domains has
been engendered by a strong and vibrant user community.
Anecdotally, these users likely chose SymPy because of its ease of access.

>>>>

SymPy expressions are immutable trees of Python objects. SymPy uses Python both
as the internal language and the user language. This permits users to access to
the same
methods that the library implements in order to extend it for their needs.
Additionally, SymPy has a powerful assumptions
system for declaring and deducing mathematical properties of expressions.

SymPy supports a wide array of mathematical facilities. This includes functions for
simplifying expressions, performing common calculus operations, pretty printing
expressions, solving equations, and representing symbolic matrices. Other supported
facilities
include discrete math, concrete math, plotting, geometry, statistics,
polynomials, sets, series, vectors, combinatorics, group theory, code
generation, tensors, Lie algebras, cryptography, and special functions.
Additionally, SymPy contains submodules targeting certain specific domains,
such as classical mechanics and quantum mechanics.  This breadth of domains has
been engendered by a strong and vibrant user community.
Anecdotally, these users likely chose SymPy because of its ease of access.
